---
title: "Data_Clean"
date: "2023-06-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task: Statistics

```{r}
library(readr)
PatVis <- read.csv('patients_visits.csv')
head(PatVis)
```

### Sub task 1

Is the BMI different between the healthy and control group?

```{r}
library('ggplot2')
ggplot(data=PatVis, aes(x=Disease, y=BMI, group=Disease)) + geom_violin()
```
```{r}
suppressPackageStartupMessages(library(dplyr))
by_dis <- PatVis %>% group_by(Disease)
res <- t.test(BMI ~ Disease, data = by_dis)
res
```
Conclusion: BMI doesn't differ significantly between the groups.

### Sub task 2

Is the proportion of Smoke status different between the healthy and control group?

```{r}
table(PatVis$Disease, PatVis$Smoking_status)
chisq.test(PatVis$Disease, PatVis$Smoking_status, correct=FALSE)
```
Retrying because of "Chi-squared approximation may be incorrect" warning:
```{r}
D <- as.table(rbind(c(92, 214, 254), c(258, 635, 750)))
dimnames(D) <- list(health = c("diseased", "healthy"),
                    smoking = c("Current","Never","Previous"))
D
chisq.test(D)
```

Conclusion: The proportion of smoke status differs between the healthy and control group, but not on a significant level.

### Sub task 3

Is the smoke status related to the number of Hospital visits regardless of the disease?

```{r}
anova_graph <- ggplot(data = PatVis, mapping = aes(x = Smoking_status, y = Visit_No)) + geom_boxplot()
anova_graph
```

```{r}
anova_model <- aov(data = PatVis, formula = Visit_No ~ Smoking_status)
summary(anova_model)
```

Conclusion: The smoke status does not seem to be related to the number of hospital visits.

### Sub task 4

Is the number of visits higher in the Disease group than in the Healthy group?

```{r}
by_dis <- PatVis %>% group_by(Disease)
res <- t.test(Visit_No ~ Disease, data = by_dis)
res
```

Conclusion: Hospital visits do not significantly differ between the groups.

### Sub task 5

Do Males have a higher current smoke percentage compared to Females?

```{r}
table(PatVis$Sex, PatVis$Smoking_status, exclude="Prefer not to answer")
```
```{r}
M <- as.table(rbind(c(106, 529), c(244, 1324)))
dimnames(M) <- list(sex = c("Female", "Male"),
                    smoking = c("Current","Never or previous"))
M
chisq.test(M)
```

Conclusion: The current smoking percentage does not differ significantly between males and females (~15.5% in males and ~16.7% in females).