---
title: "R Exercise"
date: "2023-05-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

Loading some data about iris species (Schwertlilien) with a little help from <https://www.kaggle.com/code/leolcling/visualizing-iris-datasets-with-r-ggplot2/notebook>. The first 6 rows are shown.

```{r}
library('ggplot2')
library(readr)
options(repr.plot.width = 6, repr.plot.height = 6) # resize the plots 
Iris <- read.csv('iris.csv') # downloaded from https://gist.github.com/netj/8836201
class(Iris) 
head(Iris)
```

## Scatter Plot

A scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species shown in different colors

```{r}
ggplot(data=Iris,aes(x=sepal.length, y=sepal.width, color=variety)) + geom_point(size = 4)
```

### Regression Line

A regression line for the previous plot with the whole data set (regardless of the species)

```{r}
ggplot(data=Iris,aes(x=sepal.length, y=sepal.width)) + geom_point(size = 4) + geom_smooth(method = "lm", se=FALSE)
```

### Pearson correlation

The Pearson correlation for this plot

```{r}
cor(Iris$sepal.length, Iris$sepal.width)
```

## Box plot

A box plot for Petal.Width with 3 species separately in the x-axis in different colors

```{r}
ggplot(data=Iris, aes(x=variety, y=petal.width, color=variety)) + geom_boxplot()
```

## Histogram

A histogram for Petal.Width with 3 species separately in x-axis in different colors

```{r}
ggplot(data=Iris, aes(x=petal.width, fill=variety)) + geom_histogram()
```

## T-test

A t-test of Petal.Width between species setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species. Some helpful info on this was found in <http://www.sthda.com/english/wiki/unpaired-two-samples-t-test-in-r>

```{r }
# load data from csv that only includes petal.width and species setosa and virginica
Petals <- read.csv('iris2.csv')
class(Petals) 
res <- t.test(petal.width ~ variety, data = Petals, var.equal = TRUE)
res
```

The p-value is smaller than 0.05, so it is significant (conditions for applicability of t-test have not been checked).
